The K2 Bright Star Survey

### 2019-05-16 paper/ms.tex
brite citations

Using the Sydney pipeline \citep{Huber2009} with modifications to the extraction of \Dnu detailed in \citep{Yu2018}, we extract the global asteroseismic parameters \numax and \Dnu for all 31 giants for which oscillations are detected. These parameters are listed in Table~\ref{rgs}. High precision spectroscopy of these stars would permit detailed stellar modelling and the extraction of precise elemental abundances, which would make these stars valuable as benchmarks for large spectroscopic surveys or testing detailed stellar models. This sample would be a valuable addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J} and the~33 \kepler Smear Campaign spectroscopic benchmark red giants (Pope et al., 2019, under review).

>>>>

Using the Sydney pipeline \citep{Huber2009} with modifications to the extraction of \Dnu detailed in \citep{Yu2018}, we extract the global asteroseismic parameters \numax and \Dnu for all 31 giants for which oscillations are detected. These parameters are listed in Table~\ref{rgs}. High precision spectroscopy of these stars would permit detailed stellar modelling and the extraction of precise elemental abundances, which would make these stars valuable as benchmarks for large spectroscopic surveys or testing detailed stellar models. This sample would be a valuable addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J}, the 23 BRITE-Constellation asteroseismic giants \citep{Kallinger2019}, and the~33 \kepler Smear Campaign spectroscopic benchmark red giants (Pope et al., 2019, under review).
